%-------------------------
% Resume in Latex
% Author : Gennadii Chursov
% Based off of: https://github.com/sb2nov/resume and https://www.overleaf.com/latex/templates/jakes-resume/syzfjbzwjncs
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape PIYUSH AGARWAL} \\ \vspace{1pt}
    \small \textit{Applied Data Scientist I} \\
    +91-7976072019 $|$ \href{mailto:namesurname@gmail.com}{\underline{agarwalpiyush626@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/namesurname/}{\underline{linkedin.com/in/\href{https://www.linkedin.com/in/piyush-\%20\%20\%20\%20\%20\%20agarwal-376b84194}{piyush-agarwal-376b84194}/}} $|$
    \href{https://github.com/namesurname}{\underline{github.com/piyush626}}
\end{center}

%-----------SUMMARY-----------
\section*{Summary}
Applied Scientist with strong knowledge in Data Science, Machine Learning, Deep Learning, Natural Language Processing, Python, SQL, Computer Vision, Generative AI and LLMs and having proven track record of delivering impactful solutions and driving business growth through advanced analytics techniques, strong problem-solving skills. Being an AI practitioner , I am passionate about leveraging advanced analytics and AI technologies to solve complex problems and drive data-driven decision-making. I stay updated with the latest trends in the field and continually enhance my skills to stay at the forefront of innovation. I am seeking opportunities to work with forward-thinking organizations that value data-driven approaches and embrace the transformative power of AI. I am eager to contribute to cutting-edge projects that push the boundaries of data science, making a tangible impact. 

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, SQL, Java} 
     \\
    \textbf{Statistics}{: Descriptive Stats, Inferential Stats, Data Analysis, Feature Engineering, Insights Extraction and Summarisation.}
    \\
    \textbf{Machine Learning}{: Linear Regression, Logistic Regression, Decision Trees, Random Forests, Naive Byes, SVM, Bagging and Boosting, XGBoost, KMeans Clustering, DBSCAN Clustering, KNN Classifier.}
    \\
    \textbf{Deep Learning and NLP}{: Artifical Neural Networks, Convolutional Neural Networks, Recuurent Neural Networks, Transformers, Activation Functions, Optimisers, Cost Functions, Word Embedding.}
    \\
     \textbf{Libraries and Frameworks}{: TensorFlow, Keras, Pytorch, LangChain, LlamaIndex, OPENAI API, Hugging Face, Pandas, Numpy, SciKit Learn, NLTK, SciPy, Seaborn.} \\
     \textbf{Tools}{: Jupyter Lab, Visual Studio, Pycharm, Git, Colab, Command Promt, AWS/S3, Confluence, Jira.}
    }}
 \end{itemize}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Applied Scientist I}{Jan 2024 -- Current}
      {Tekion, Cloud Native Automative Plateform}{Bangalore, India}
      \resumeItemListStart
      \resumeItem{Analytics GPT Insights :- Worked on to leverage OPENAI capabilities for Insights and Summarization tasks and built Business actionable Insights delivery to clients leveraging the power of GPT. Provided clients monthly expense/gross insights across different dealership's departments and across different time frames.
    }
    \resumeItem{Driving License Scanner and Validation :- Built identity document detail extraction and authentication for business clients to automate the process of check-in fast and avoid forgery. Able to achieve 94 percent accuracy across 30 US states' identities cards with the help of LayoutLMV3 Model.
    }
    \resumeItemListEnd

    \resumeSubheading
      {Associate Applied Scientist}{Jan 2022 - Dec 2023}
      {Tekion, Cloud Native Automative Plateform}{Bangalore, India}
      \resumeItemListStart
        \resumeItem{Vehicle Parts Recommendation:- Created impactful recommendations that helped service advisors to quickly select relevant and precise parts for different jobs need to be done for vehicle servicing. Able to achieve 95 percent recommendation predictive power with moderate coverage(Organizational paid service data i.e ~45 percent of OEMs data) of vehicle service transactions.
        }
        \resumeItem{Vehicle Propensity and Service Recommendation :- Worked on  propensity of products by driving out useful insights/variables from the data. Improved performance to 93 percent with the help of feature engineering and XgBoost technique, which really helped dealerships to maintain inventory for sales for next three months, along with service parts to be used most in upcoming services.
        }
        \resumeItem{General Ledger Account Mapping :- Created the G/L Account Mapping tool to automate accounting ledgers and to increase the efficiency of tech-team. Reduced time to 4 hours from 3-4 days. Able to cover 80 percent transactions with 95 percent accuracy with the help of Random Forest Classifier and Heuristic approach.
        }
        \resumeItem{Invoice User Preference :- Worked on User Preference Services for Invoice Management of vendors which is also based on LayoutLMV3 document detail extraction, and tweaked the uncovered areas with user based approach. Created a great impact for the clients.
        }
      \resumeItemListEnd

      \resumeSubheading
      {Data Scientist Intern}{Aug 2021 - Dec 2021}
      {HighRadius, Autonomous Finance Platform}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Worked on Account Receivables and Account Payables Data to find out and forecast accounting insights and patterns.}
        \resumeItem{Refined Code-Bases and Performed test cases to validate and increase coverage of pipelines.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
% \section{Projects}
%    \resumeSubHeadingListStart
%      \resumeProjectHeading
%          {\textbf{Gitlytics} $|$ \emph{Python, Flask, React, PostgreSQL, Docker}}{June 2020 -- Present}
%          \resumeItemListStart
%            \resumeItem{Developed a full-stack web application using with Flask serving a REST API with React as the frontend}
%            \resumeItem{Implemented GitHub OAuth to get data from user’s repositories}
%            \resumeItem{Visualized GitHub data to show collaboration}
%            \resumeItem{Used Celery and Redis for asynchronous tasks}
%          \resumeItemListEnd
%      \resumeProjectHeading
%          {\textbf{Simple Paintball} $|$ \emph{Spigot API, Java, Maven, TravisCI, Git}}{May 2018 -- May 2020}
%          \resumeItemListStart
%            \resumeItem{Developed a Minecraft server plugin to entertain kids during free time for a previous job}
%            \resumeItem{Published plugin to websites gaining 2K+ downloads and an average 4.5/5-star review}
%            \resumeItem{Implemented continuous delivery using TravisCI to build the plugin upon new a release}
%            \resumeItem{Collaborated with Minecraft server administrators to suggest features and get feedback about the plugin}
%          \resumeItemListEnd
%    \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {CHANDIGARH UNIVERSITY}{Mohali, India}
      {Bachelor of Engineering, Computer Science (AI-ML)}{2018 - 2022}
  \resumeSubHeadingListEnd
  \resumeSubHeadingListStart
    \resumeSubheading
      {SDP SR. SEC. SCHOOL}{JhunJhunu, India}
      {Higher Secondary Education}{2016 - 2017}
  \resumeSubHeadingListEnd
  \resumeSubHeadingListStart
    \resumeSubheading
      {SDP SR. SEC. SCHOOL}{JhunJhunu, India}
      {Secondary Education}{2014 - 2015}
  \resumeSubHeadingListEnd

%-----------Certifications-----------
\section{Certifications}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Machine Learning - Coursera} \\
     \textit{Relevant courseworks - Supervised Learning Algorithms, Unsupervised Learning Algorithms, Exploratory Data Analysis Best Practices} \\
     \textbf{Neural Networks and Deep Learning - Coursera} \\
     \textit{Relevant courseworks - Mathematics behind Neural Networks, Working of Neural Nets, Forward Propagataion, Backward propagation} \\
     \textbf{Improving Deep Neural Networks: Hyperparameter tuning, Regularization and Optimization - Coursera} \\
     \textit{Relevant courseworks - Activation Functions, Loss Functions, Optimisers, Hyperparameter Tuning, Regularisation for improving performance of Neural networks} \\
     \textbf{Sequence Models - Coursera} \\
     \textit{Relevant courseworks - Introductions to Recurrent neural networks and journey to attention mechanism} \\
     \textbf{Data Science and Machine Learning Training - InternShala} \\
     \textit{Relevant courseworks - Practical Learning of Machine Learning and Data Exploration} \\
    }}
 \end{itemize}


%-----------Interests and Participations-----------
 \section{Extracurriculars}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Participations} \\
     \textit{Attended IAF SSB, Dehradun}\\
     \textit{Participated in Machine Learning Hackathons conducted by Analytics Vidhya}\\
     \textit{Elected as the leader of the house to conduct events and assembly during HSE)}\\
     \textit{Attended various seminars organized by Chandigarh University on Corporate, Competitive and Spiritual World)} \\
     \textit{Elected as the leader of the Badminton Team to represent in the interSchool BCT)}\\
     \textbf{Interests} \\
     \textit{Financial Markets and Trading | Travelling | Sports | Reading Blogs on Technologies | Music}\\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
